Data_visualization

### 2018-11-03 Manuscript_draft/Manuscript_draft.Rmd
changes

The effect of heterospecific pollen has been widely studied (Morales & Traveset 2008). Native species are supposed to have greater negative effect than native ones @arceo2016. However, the quantity of pollen that integrates in the network can be quite low @bartomeus2008. Moreover, closely related species are supposed to reduce fitness in greater effect but the evidence is scarce and based on independent studies with different methodologies (Arceo-gomez & Ashman 2016) or studies that just check it with a pair of species that are highly related with the aim to understand hybridization costs (refs). There is a need to deepen into how relatednes is involve in the costs of heterospecific pollen effect. Furthermore, following the conceptual trait framework of Ashman and Arceo-Gomez on heterospecific pollen there are good theoretical basis for trait effect. Notwithstanding, non empirical work has tested how really these traits are involved in heterospecific pollen effect.

>>>>

The effect of heterospecific pollen has been widely studied (Morales & Traveset 2008). Invasive species are supposed to have greater negative effect than native ones @arceo2016. Although when non-natives species don´t have greater negative effect we still don´t know why. For this reason, this ecological question is non a native non native one is a trait based issue that is still to be solved. Moreover, the quantity of pollen that integrates in the network can be quite variable ranging from low quatities @bartomeus2008 to intermediate (ref) to high (ref). Moreover, closely related species are supposed to reduce fitness in greater effect but the evidence is scarce and based on independent studies with different methodologies (Arceo-gomez & Ashman 2016) or studies that just check it with a pair of species that are highly related with the aim to understand hybridization costs (refs). There is a need to deepen into how relatednes is involve in the costs of heterospecific pollen effect. Furthermore, following the conceptual trait framework of Ashman and Arceo-Gomez on heterospecific pollen there are good theoretical basis for trait effect. Notwithstanding, non empirical work has tested how really these traits are involved in heterospecific pollen effect.

Explain traits. Put examples

### 2018-11-03 Manuscript_draft/Manuscript_draft.tex
changes

The effect of heterospecific pollen has been widely studied (Morales \&
Traveset 2008). Native species are supposed to have greater negative
effect than native ones Arceo-Gómez and Ashman (2016). However, the
quantity of pollen that integrates in the network can be quite low
Bartomeus et al. (2008). Moreover, closely related species are supposed
to reduce fitness in greater effect but the evidence is scarce and based
on independent studies with different methodologies (Arceo-gomez \&
Ashman 2016) or studies that just check it with a pair of species that
are highly related with the aim to understand hybridization costs
(refs). There is a need to deepen into how relatednes is involve in the
costs of heterospecific pollen effect. Furthermore, following the
conceptual trait framework of Ashman and Arceo-Gomez on heterospecific
pollen there are good theoretical basis for trait effect.
Notwithstanding, non empirical work has tested how really these traits
are involved in heterospecific pollen effect.

>>>>

The effect of heterospecific pollen has been widely studied (Morales \&
Traveset 2008). Invasive species are supposed to have greater negative
effect than native ones Arceo-Gómez and Ashman (2016). Although when
non-natives species don´t have greater negative effect we still don´t
know why. For this reason, this ecological question is non a native non
native one is a trait based issue that is still to be solved. Moreover,
the quantity of pollen that integrates in the network can be quite
variable ranging from low quatities Bartomeus et al. (2008) to
intermediate (ref) to high (ref). Moreover, closely related species are
supposed to reduce fitness in greater effect but the evidence is scarce
and based on independent studies with different methodologies
(Arceo-gomez \& Ashman 2016) or studies that just check it with a pair
of species that are highly related with the aim to understand
hybridization costs (refs). There is a need to deepen into how
relatednes is involve in the costs of heterospecific pollen effect.
Furthermore, following the conceptual trait framework of Ashman and
Arceo-Gomez on heterospecific pollen there are good theoretical basis
for trait effect. Notwithstanding, non empirical work has tested how
really these traits are involved in heterospecific pollen effect.

Explain traits. Put examples

### 2018-11-03 Rmd/Data_visualization_common_names.Rmd
Fixing colours plot
changes

*Abstract*

@@

@@

#load libraries
library(reshape2)
library(ggplot2)
library(dplyr)
library(gridExtra)
library(grid)
library(lattice)
library(gtable)
##
###
#B. OLERACEA
###
##
#

>>>>

# Abstract

@@

# Results

First I show numerical results

Proof firstly the effect of hp respect the cross... DO IT!

To test the possible relationships between heterospecific pollen effect and phylogenetic distance we have performed Mantel test between the scaled distance matrix of effect (hand-cross pollination substracted by the mean heterospecifc pollen effect) and the evolutive distances (calculated with both ITS and RBCL markes, obtaining similar results). Following Letten & Cornwell 2015 check other ref we have compare it with square root of the evolutive distance matrix.

Post here results...

```{r, message=FALSE, warning=FALSE, size='tiny'}
read.csv("Data/matrix_scale_effect.csv", row.names=1, header=T)
```

Check with traits!! I still have to work more on them

@@

#load libraries
library(reshape2)
library(ggplot2)
library(dplyr)
library(gridExtra)
library(grid)
library(lattice)
library(gtable)

##
###
#B. OLERACEA
###
##
#
